Market-based Mechanisms for Resource Scheduling

### 2013-12-17 paper/paper.tex
Write a little bit more

\subsection{Bidding policy}
Given a set of tasks it wishes to run, the framework must

>>>>

\subsection{Bidding policy}
Within our setting, the framework must associate a willingness to pay with each
task it wishes to run. We now describe some reasonable ways for the frameworks
to do so.

\paragraph{Default policy} For backwards compatibility, we want to be able to
use existing Mesos frameworks which are not aware of prices. For these, we
define a default bidding policy which assumes that all tasks are equally
important.

Intuitively, a framework with higher income can afford to have a higher
willingness to pay. A framework which has accumulated a lot of money can also
afford to pay more, at least for a limited amount of time before its balance is
exhausted. Also, tasks which require more resources should have a
correspondingly higher willingness to pay.
